### 2008-12-20 talk/ecoop2009/rainbow.tex
I guess this was a typo

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval(code, pc, args, pool):
    code_len = len(code)
    stack = []
    while pc < code_len:
        opcode = ord(code[pc])
        opcode = hint(opcode, promote_class=True)
        pc += 1

>>>>

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval(code, pc, args, pool):
    code_len = len(code)
    stack = []
    while pc < code_len:
        opcode = ord(code[pc])
        opcode = hint(opcode, concrete=True)
        pc += 1
